---
title: 'Differential Expression with RNA-Seq - GrasPods Tutorial'
author: "Rod Docking"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
bibliography: ../data/references.bib
---

```{r setup, include=FALSE, results="hide", warning=FALSE}
# Load tidyverse up-front to set base_size for plots
library(tidyverse)
theme_set(theme_bw(base_size = 18))
# Required for chunk options
library(knitr)
opts_chunk$set(fig.path = '../plots/paper-',
               cache.path = '../cache/report-',
               dev=c("png","pdf"),
               fig.width = 14,
               fig.height = 7,
               dpi = 300,
               fig.show = 'hold',
               fig.lp = "fig:",
               cache = TRUE,
               par = TRUE,
               echo = TRUE,
               results = "hide",
               message = FALSE,
               warning = FALSE)
```

## Goals

The goal of this tutorial is to help students gain familiarity with differential gene expression analysis using RNA-Seq data. To do this, we will work through a recent tutorial article [@Law2016-iu]. 

## Setup

### 2017-07-20

#### Setup Sub-task 1

- Describe any initial setup tasks like:
	- Finding previous analysis tickets or reports
	- Setting up DB connections
	- Determining appropriate libraries to use for the analysis

#### Setup Sub-task 2

## Analysis Task

### 2017-07-20

#### Analysis Sub-task 1

- Describe analysis tasks in enough detail so that your future self can
understand both _how_ and _why_ a particular analysis was conducted
- Chunks of code necessary for the analysis can be included directly:

```{r example_r_chunk, echo=TRUE, include=TRUE, results="markup", warning=FALSE}
# An example chunk of R code
# Chunk options reference: http://yihui.name/knitr/options/
rnorm(10)
```

```{bash example_bash_chunk, echo=TRUE, include=TRUE, results="markup", warning=FALSE}
# An example chunk of bash code
# Note that it's usually _not_ a good idea to do this, but it's possible
echo 'I am the egg man, they are the egg men.'
```

```{python example_python_chunk, echo=TRUE, include=TRUE, results="markup", warning=FALSE}
# An example chunk of python code
# Note that it's usually _not_ a good idea to do this, but it's possible
print 'I am the walrus, goo goo g\'joob g\'goo goo g\'joob.'
```

#### Analysis Sub-task 2

## Conclusion

- Summarize the analysis:
	- Was the goal described above achieved?
	- What was the resolution of the issue being analyzed?
	- What's next? More analysis (if so, where?)
